Rotating Stars from \Kepler Observed with Gaia DR2

### 2018-05-14 paper/ms.tex
friday writing:

%Rotation periods in this study come from \citet{mcquillan2014}, who performed an Auto-Correlation Function analysis of \Kepler stars cooler than 6500 K that had at least $\sim$2 years of observation. The periods recovered from this approach generally agree very well with those found via Lomb-Scargle Periodograms \citep[e.g.][]{reinhold2013,aigrain2015}. Sources with multiple distinct periods, such as from binary systems with two spotted stars \citep[e.g.][]{lurie2015} are detected by \citet{mcquillan2014}, but are not included in the following analysis.

%The Gaia Data Release 1 (DR1) provides astrometric positions for over $10^9$ sources from the first year of observation with Gaia. The Tycho-Gaia Astrometric Solution (TGAS) measures improved proper motions and parallaxes for 2 million nearby, bright sources by extending the astrometric solutions from Tycho and Hipparcos. While the TGAS data are not a complete astrometric survey, and have possible systematics in the reported parallaxes \citep{gaia_dr1,stassun2016}, they represent a significant improvement in the astrometry and kinematics available for stars in the \Kepler field.

Our 
data xmatched by M. Bedell between \Kepler and Gaia DR2 (CITE). using 1arcsec radius, which included 195,830 sources with stellar properties from the \Kepler Data Release 25 and {\em Gaia} DR2.

sub-set was matched to the rotation catalog of \citet{mcquillan2014}

@@

distances using the updated prescription from \citet{bailer-jones2018}
Following the suggested use of \citet{bailer-jones2018}, we use only sources with {\tt modality\_flag} == 1 (i.e. not a bimodal distance solution) and {\tt result\_flag} == 1 (i.e. well constrained distance).

>>>>

We used the largest homogeneous catalog of rotation periods available from the \Kepler mission. The sample from \citet{mcquillan2014} provides rotation periods for more 34,030 stars, measured using the Auto-Correlation Function (ACF). While the ACF does not have as fine of resolution in recovering periods as compared with methods such as the Lomb-Scargle Periodogram, it is more robust to detecting the true period as opposed to an alias, and more complete for batch analysis of all stars \citep[e.g. see][]{aigrain2015}.

The \Kepler data was matched to the {\em Gaia} DR2 source catalog using a 1 arcsecond radius. We used the \Kepler--Gaia cross-match made publicly available by M. Bedell, which included entries for 195,830 sources. \Kepler-based stellar parameters included in this cross-match come the Data Release 25 \Kepler catalog. Joining this cross-matched table to the \citet{mcquillan2014} catalog, we found 33,538 sources.

@@

Rather than simply use the inverse {\em Gaia} parallax values to measure the distance to sources, we use the improved distance prescription from \citet{bailer-jones2018}, who provided independent distances estimates for 1.33 billion {\em Gaia} sources using a weak prior on the distribution of stars in our galaxy. We follow their suggested use of the distance catalog, we only include sources with {\tt modality\_flag} == 1 (i.e. not a bimodal distance solution) and {\tt result\_flag} == 1 (i.e. well constrained distance).
